On Cybersecurity\\Science and Engineering\footnote{Confidential, restricted to the authors. Property of V-Research S.r.l.}

### 2020-04-08 engineering.tex
full review of engineering section

Several standards mandates a secure-by-design approach in which 
cybersecurity shall be considered at the very early stages of the 
design process. For example,
\begin{enumerate}[noitemsep]
	\item DO-326A -- ``Airworthiness Security Process Specification''
		requires a cybersecurity risk assessment of the design and is
		the ``are the only Acceptable Means of Compliance (AMC) by FAA
		\& EASA for aviation cyber-security airworthiness certification,
		as of 2019'' as pointed out by SAE in \autocite{SAE2019DO326A}.
	\item NIST 800-82 \autocite{Stouffer2011guide} -- ``guide to Industrial
		Control System (ICS) Security''
	\item J3061:2016-1 \autocite{SAE2016J3061} -- ``Cybersecurity Guidebook
		for Cyber-Physical Vehicle Systems'' defines ``set of
		high-level guiding principles for Cybersecurity as it relates
		to cyber-physical vehicle systems'' and states that
		``incorporate Cybersecurity into cyber-physical vehicle systems
		from concept phase through production, operation, service, and
		decommissioning''
\end{enumerate}
Companies who develop CPS (e.g. aerospace systems or elevator systems), must adhere
to strict regulations and quality assurances processes. Introducing tools and procedures 
in their processes requires a detailed and justified overview on how those
tools and procedures can be used. In Figure~\ref{fig:spdl}, we provide an overview
of a process that consider cybersecurity in the specification, design, and implementation
stages. The overall process start with the specification of the architectural (both physical
and functional) requirements from which the Weaknesses are automatically identified.
Based on the Assets, architectures, and the Weaknesses the cybersecurity risk is
calculated based on the $\abftheory$-theory. An iterative process between 
the user (e.g. the engineer) and the \secramod{} module of the \abftool{} allows the user to move to the design phase
when the risk level is considered acceptable. The design phase starts by automatically mapping
the Weaknesses into Vulnerabilities which are, in turn, fed into the \designverifmod{}
module along with the final specification. The Module returns a list of Vulnerabilities and
potential Mitigations. The user then procees in implementing the CPS and the SW/HW choices
can be tested by the \atgmod. \fix{mr}{While we have described the overall view, from
specificaiton to implementation, in this text we only consider the process from specificaiton to design.}

@@

@@

\begin{definition}{\bf Functional Block and Architecture --}\label{def:funblock}
	A functional block of an agent $a$ 
	takes a region of input-Beliefs and outputs a region of output-Beliefs. 
	A functional architecture is an interconnected system of functional blocks.
\end{definition}
The quality of a functional block or architecture cannot be expressed as a relation 
between input and output belief since there is a transformation process in the functional
block which will be defined during the design and implementation phase, but not
necessarily known in details in the specification phase. In order to
define the quality of functional block we first need to introduce the engineering concept of
Facts.

\Paragraph{Requirements as Facts}
During the specification phase, for any agent, channel, port, functional block
and architecture, there exist a Fact predicating over them.
In other words, any requirement is defined as a Fact since they must be true in
any design or implementation. As we stated in Section~\ref{sec:theory} and depicted in
Figure~\ref{fig:soundness}, Facts are strategic rules that defines how
the system shall behave (by specification), while reality may be shown to
be insecure.

@@

\begin{definition}{\bf Secure Functional Block and Architecture --}\label{def:secfun}
	A functional block is secure if the input beliefs and output beliefs
	are in $EQ$ relation with the corresponding Facts mandated by requirements.
	A functional architecture composed exclusively by secure functional blocks
	is considered secure.
\end{definition}

Therefore, there exists the following weaknesses in the functional
architecture, where $\beliefRegion_I$ and $\beliefRegion_O$ are input and
output Beliefs respectively, and $\factRegion_I$ and $\factRegion_O$ are
the corresponding Facts (i.e. what really happens). 
\begin{itemize}
	\item $\eq{\beliefRegion_I}{\factRegion_I}$ and then only specified
		inputs can be fed to the functional block but:
	\begin{enumerate}[start=49, label={W\arabic*)}]
		\item $\dr{\beliefRegion_O}{\factRegion_O}$, not all the specified
			outputs are produced
		\item $\po{\beliefRegion_O}{\factRegion_O}$ , only some but not all of the specified
			outputs are produced along with some non-specified output are produced
		\item $\pp{\beliefRegion_O}{\factRegion_O}$ , not all the specified outputs are produced 
		\item $\ppi{\beliefRegion_O}{\factRegion_O}$ , not all the output have been specified
	\end{enumerate}
	\item $\po{\beliefRegion_I}{\factRegion_I}$, not all the specified inputs can be fed into the functional block
	\begin{enumerate}[start=53, label={W\arabic*)}]
		\item $\dr{\beliefRegion_O}{\factRegion_O}$
		\item $\po{\beliefRegion_O}{\factRegion_O}$
		\item $\pp{\beliefRegion_O}{\factRegion_O}$
		\item $\ppi{\beliefRegion_O}{\factRegion_O}$
		\item $\eq{\beliefRegion_O}{\factRegion_O}$ this case implies
			that somehow there is no input that generates an
			non-specified output but this is not because the inputs
			are secure 
	\end{enumerate}
	\item $\pp{\beliefRegion_I}{\factRegion_I}$, not all the specified
		inputs can be fed into the block
	\begin{enumerate}[start=58, label={W\arabic*)}]
		\item $\dr{\beliefRegion_O}{\factRegion_O}$
		\item $\po{\beliefRegion_O}{\factRegion_O}$
		\item $\pp{\beliefRegion_O}{\factRegion_O}$
		\item $\ppi{\beliefRegion_O}{\factRegion_O}$
		\item $\eq{\beliefRegion_O}{\factRegion_O}$
	\end{enumerate}
	\item $\ppi{\beliefRegion_I}{\factRegion_I}$, not all the inputs that
		can be fed into the functional block follows the specification
	\begin{enumerate}[start=63, label={W\arabic*)}]
		\item $\dr{\beliefRegion_O}{\factRegion_O}$
		\item $\po{\beliefRegion_O}{\factRegion_O}$
		\item $\pp{\beliefRegion_O}{\factRegion_O}$
		\item $\ppi{\beliefRegion_O}{\factRegion_O}$
		\item $\eq{\beliefRegion_O}{\factRegion_O}$
	\end{enumerate}
	\item $\dr{\beliefRegion_I}{\factRegion_I}$, no specified inputs can be
		fed into the functional block
	\begin{enumerate}[start=68, label={W\arabic*)}]
		\item $\dr{\beliefRegion_O}{\factRegion_O}$
		\item $\po{\beliefRegion_O}{\factRegion_O}$
		\item $\pp{\beliefRegion_O}{\factRegion_O}$
		\item $\ppi{\beliefRegion_O}{\factRegion_O}$
		\item $\eq{\beliefRegion_O}{\factRegion_O}$
	\end{enumerate}
\end{itemize}

\subsubsection{Security Requirements} 
While standards (such
as IEC62443-1-3\fixnote{mr}{check the correct version}) defines requirements as
``information in transit/at-rest should be encrypted'' we believe that, at
specification level, security requirements can be formulated as subcategories of
the well-known CIA triad (where CIA stands for Confidentiality, Integrity,
Availability).
Infosec, or Information Security, defines the security risks related to
information with the de-facto standard CIA triad, which is often criticized
\autocite{CIAcriticismCPS} for being too general or non-adequate (e.g. by
adding authenticity which is often used as a building block for confidentiality
and integrity) to be effectively applied to the engineering of systems. Due to
this, many researchers and organization tried to improve the CIA triad.  The
evolutions/extensions of the CIA triad has been documented, e.g., in
\autocite{Samonas2014cia} and is summarized in Table~\ref{tab:ciaevolution}.

An representative example is the effort made by the OECD (Organisation for Economic
Co-operation and Development) in \autocite{OECD2013guidelines} to define
security guidelines for information system (1992) based on new principles such
as ``awareness, ethics, risk assessment'' and maintain those revising the
document (e.g.  following the multistakeholder expert consultation in 2013).
Other similar efforts focused on defining entirely new principles or extending
the CIA triad, such as \autocite{NISTSP800-160}. What is of interest for our
argument is that, to the best of our knowledge, all of the approaches that aim
at improving the CIA triad are besed on motivations related to empirical evidences. On the contrary,
we now define (in Section~\ref{sec:properties}) the CIA triad for an agent
defined in the $\abftheory$-theory and we test if (i) other properties are
allowed in the $\abftheory$-theory, and (ii) if and how the CIA triad can be
detailed in the $\abftheory$-theory.

In \autocite{Anderson1972report,Samonas2014cia}, CIA are defined as follows.
\begin{itemize}
	\item Unauthorized information release: an unauthorized person is able
		to read and take  advantage  of  information  stored  in  the
		computer.  This  category of concern  sometimes  extends  to
		``traffic  analysis,''  in  which  the intruder  only observes
		the  patterns  of  information  use.  From  those patterns,
		the  intruder can   infer   some   information   content.
		This category   also   includes   the unauthorized use of a
		proprietary program.  (Confidentiality or Secrecy) 
	\item Unauthorized  information  modification:  an  unauthorized person
		is  able  to make changes in stored information -- a form  of
		sabotage.  It should be noted that in the case of this kind of
		violation, the intruder does not necessarily see the
		information he has changed.  (Integrity)
	\item Unauthorized  denial  of  use:  an  intruder  can  prevent  an
		authorized  user  from referring to, or from modifying
		information, even though the intruder may not be able to refer
		to, neither modify the information themselves. (Availability)
\end{itemize}

We now want to generalize the CIA triad to agents and not just 
information and map it to the $\abftheory$-theory. For the sake of simplicity,
we revert the order and start from availability.

\Paragraph{Availability and Integrity (Architecture Security)}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{client-server.pdf}
	\caption{Client-Server paradigm in $\abftheory$-theory}
	\label{fig:client-server}
\end{figure}
Availability, again, is the denial of use of a resource. In the $\abftheory$-theory, 
in order to prevent a resource to be available, there
exists only (i.e. inclusively) the following mutually exclusive cases
that we illustrate using a client-server paradigm (depicted in Figure~\ref{fig:client-server}).
\begin{enumerate}
	\item\label{case:srv1} The resource on the server cannot be found, so that it is
		possible for the client to contact the server and the server
		sends a response back, but the output-port does not receive the
		necessary information. This may be due to a software error such
		that the functional architecture doesn't output a response, or
		a problem in the flow of information (i.e. the functional
		architecture doesn't receive the necessary information from
		other resources), or an hardware failure \&c. This is formalized
		as the relation between the beliefs produced by the functional
		architecture and the ones received by the output port, i.e.
		$\rcc(\behaviorRegion_s,\{\text{res}\})$ or 
		$\rcc(\beliefRegion_s,\{\text{res}\})$ 
	\item\label{case:srv2} The server hosting the resource is down, and then the server
		cannot output responses (i.e. insecure output port due to drop-related issue) or receive
		requests (insecure input port due to drop-related issue) or both.
	\item\label{case:srv3} The client cannot properly compute request (simmetrically to Case~\ref{case:srv1})
	\item The client is down, symmetric to Case~\ref{case:srv2}
	\item The channel is down due to a drop related issue in one of the two channels 
\end{enumerate}
%All the cases but Case~\ref{case:srv1} and Case~\ref{case:srv3}, tell us how to map the
%property of availability over the weaknesses of ports and communications.  The
%Cases~\ref{case:srv1} and~\ref{case:srv3}, are exceptions because the formulas $res$ and $req$ 
%detail the specification with a singleton instead of a region of formulas (or, better, $|res|$ is equal to the one of the
%base).
%In other words, a channel, a port, an entity, or a functional block are
%Fact (stated in a factorial way) and not Beliefs; what they produce or 
%their non-specified internals are Beliefs.  In fact, we never assume an
%entity not to be in the design implementing the specification.  Similarly, when a
%functional block produces some information it produces a Belief, unless this Belief if detailed in the specification.
%For example, the server produces the Belief $res$ but the Belief given that can only be in $EQ$
%relation with the Fact $res$ (in contrast other Belief may not); therefore, $res$ is not really a belief but a Fact. 
%$res$ as a Fact is something that
%exists in the specification, while the Belief of $res$ in one of the possible
%designs may not exist. 
We shall, then, distinguish between two cases:
\begin{definition}{\bf Agent-Availability --}\label{def:agent-a}
when the property of availability is expressed over
	an agent or a system, the list of possible designs violating the
	availability property can be shown as the designs that allow drop ports
	or drop channels. 
\end{definition}\fixnote{mr}{all security definitions defines when the property is
not preserved instead of when it's preserved}
\begin{definition}{\bf Infosec-Availability --}\label{def:infosec-c}
when the property of availability is expressed
	over a formula, the list of possible designs that violates the
	availability property is reduced to the part of the system that
	influences that specific variable.
\end{definition}

\begin{definition}{\bf Agent-Integrity --}\label{def:agent-a}
when the property of integrity is expressed over
	an agent or a system, the list of possible designs violating the
	integrity property can be shown as the designs that allow insert or inject ports,
	or inert or inject channels. 
\end{definition}
\begin{definition}{\bf Infosec-Integrity --}\label{def:infosec-c}
when the property of integrity is expressed
	over a formula, the list of possible designs that violates the
	integrity property is reduced to the part of the system that
	influences that specific variable.
\end{definition}

While availability and integrity are architectural property, meaning that they
can be expressed over the behavior of a port or a channel (as constituent of
the physical or functional architecture), confidentiality is not.
Confidentiality states that an information shall not be understood and not that
the information shall not be retrieved. So, if a port leaks an entire message,
there is no confidentiality issue in general, unless that message was not
encrypted at all, in which case the confidentiality leakage is straightforward. 
On the other hand, if the
information is not provided or altered there is an availability or integrity
issue. A similar argument can be proposed for integrity sub-properties such as
authenticity or non-repudiation. No wonder why it is often stated that
availability and integrity are the first properties to be considered in CPS
while confidentiality takes the first place when dealing with security
protocols. In fact, integrity is often assumed by pattern-matching (e.g. in
AVANTSSAR \autocite{avantssar}) and availability is hardly ever considered in
protocol verification. The question is, can we express properties such as
confidentiality, authentication, or non-repudiation as architectural properties
in $\abftheory$-theory? Confidentiality (and Availability) is based on the concept 
of secrecy so we shall first start from describing what secrecy is and how it
can be used to guarantee confidentiality in a system.

>>>>

Several standards mandates a secure-by-design approach in which 
cybersecurity shall be considered at the very early stages of the 
design process. For example,
\begin{enumerate}[noitemsep]
	\item DO-326A -- ``Airworthiness Security Process Specification''
		requires a cybersecurity risk assessment of the design and is
		the ``are the only Acceptable Means of Compliance (AMC) by FAA
		\& EASA for aviation cyber-security airworthiness certification,
		as of 2019'' as pointed out by SAE in \autocite{SAE2019DO326A}.
	\item NIST 800-82 \autocite{Stouffer2011guide} -- ``guide to Industrial
		Control System (ICS) Security''
	\item J3061:2016-1 \autocite{SAE2016J3061} -- ``Cybersecurity Guidebook
		for Cyber-Physical Vehicle Systems'' defines ``set of
		high-level guiding principles for Cybersecurity as it relates
		to cyber-physical vehicle systems'' and states that
		``incorporate Cybersecurity into cyber-physical vehicle systems
		from concept phase through production, operation, service, and
		decommissioning''
\end{enumerate}
Companies which develop CPS (e.g. aerospace systems or elevator systems), must adhere
to strict regulations and quality assurances processes. Introducing tools and procedures 
in their processes requires a detailed and justified overview on how those
tools and procedures can be used. In Figure~\ref{fig:spdl}, we provide an overview
of a process that consider cybersecurity in the specification, design, and implementation
stages. The overall process start with the specification of the architectural (both physical
and functional) requirements from which the Weaknesses are automatically identified.
Based on the Assets, architectures, and the Weaknesses the cybersecurity risk is
calculated based on the $\abftheory$-theory. An iterative process between 
the user (e.g. the engineer) and the \secramod{} module of the \abftool{} allows the user to move to the design phase
when the risk level is considered acceptable. The design phase starts by automatically mapping
the Weaknesses into Vulnerabilities which are, in turn, fed into the \designverifmod{}
module along with the final specification. The Module returns a list of Vulnerabilities and
potential Mitigations. The user then procees in implementing the CPS and the SW/HW choices
can be tested by the \atgmod. \fix{mr}{While we have described the overall view, from
specificaiton to implementation, in this text we only consider the process from specificaiton to design.}

@@

As depicted in Figure~\ref{fig:atom}, so far, we have considered Information
generated by a Port $P_I$ and then sent through a channel $C$ to another
(recipient) port $P_O$. In this scenario where Ports and then Channels are
atomic (otherwise raising infinite regress), we can only  consider the
relations between Ports and Channel; considering both input-port to channel and
channel to output-port. In fact, the Weaknesses of a channel are defined in terms
of the Weaknesses of Ports. Our intention is to introduce now the concept of
functional architecture and functional blocks composing the functional architecture.
Io order to define a functional block without encountering an infinite definition,
we must reach the same conclusions as for the Channel. Therefore, describing
the information as flowing over a channel or in a functional block is purely
syntactic sugar.

\begin{figure}[t]
	\centering
	\includegraphics[width=.7\textwidth]{engineering_relations.pdf}
	\caption{Relations between Ports and Channel}
	\label{fig:atom}
\end{figure}

@@

\begin{definition}{\bf Functional Block and Architecture --}\label{def:funblock}
	A functional block of an agent $a$ 
	takes a region of input-Beliefs and outputs a region of output-Beliefs. 
	A functional architecture is an interconnected system of functional blocks.
\end{definition}
The quality of a functional block or architecture can be expressed as a
relation between input and output belief, similarly to the quality of a channel
but inverting the flow (input$\rightarrow$output instead of
output$\rightarrow$input).  One may, of course, argue that since there is a
transformation process in the functional block the quality of that
transformation process is what the theory should consider. This can
be argued not just for functional blocks (Behaviors) but also for Channels
(Assertions). As we detail afterwards, the relations considered so
far revolves around the concept of integrity or availability, while the reminder of this section 
will be focused on a broader analysis of security properties and requirements
which will also consider other security properties such as availability and
confidentiality.  In order to define the quality of the internals of a functional block or channel, we first
need to relate the concept of Facts to engineering requirements.

\Paragraph{Requirements as Facts}
During the specification phase, for any agent, channel, port, functional block
and architecture, there may exist a factorial requirement (Fact) predicating over them.
In other words, any requirement is defined as a Fact since they must be true in
any design or implementation. As we stated in Section~\ref{sec:theory} and depicted in
Figure~\ref{fig:soundness}, Facts are strategic rules that defines how
the system shall behave (by specification), while reality may be shown to
be insecure.

\Paragraph{Methodology}
We have now mapped the building blocks of our theory, namely Information,
Belief, Assertion, Behavior, and Fact. One may notice that the concept of
Knowledge hasn't been discussed in this section so far. Our argument is that
knowledge, as an epistemological concept cannot be defined due to several
implication that this would have (see, for example,
\autocite{Empiricus1990Pyrrhonism}). On the other hand, the factorial way in
which requirements are imposed may be true only in the specification, while not
necessarily true in the final implementation. While Knowledge may not be
apprehensible in general, we can define tests to see if Facts holds in a
design or implementation. What is of our interest is to guarantee security in a
system so we now correlate the potential behaviors with the standard (de-facto)
understanding of security; so that we can identify test that, at the end of the
engineering process, may not give Knowledge but, at last, tested Fact.

\subsubsection{Security Requirements} 
While standards such as IEC 62443-1-3 (the Industrial communication networks -
Network and system security -- Part 3-3: System security requirements and
security levels) defines requirements as ``confidentiality of information in
transit/at-rest'', we believe that, at specification level, a mapping
between the Infosec security concepts of the well-known CIA (Confidentiality,
Integrity, Availability) triad to the system components can be used to specify
a list of security requirements.

Infosec, or Information Security, defines the security risks related to
information as the CIA triad, which has been often criticized
(as we show afterwards) for being too general or non-adequate (e.g. by
adding authenticity which is often used as a building block for confidentiality
and integrity) to be effectively applied to the engineering of systems. Due to
this, many researchers and organization tried to improve the CIA triad.  The
evolutions/extensions of the CIA triad has been documented, e.g., in
\autocite{Samonas2014cia} and are summarized in Table~\ref{tab:ciaevolution}.

A representative example is the effort made by the OECD (Organisation for Economic
Co-operation and Development) in \autocite{OECD2013guidelines} to define
security guidelines for information system (1992) based on new principles such
as ``awareness, ethics, risk assessment'' and maintain those improving the document with
subsequent revisions 
(e.g.  following the multistakeholder expert consultation in 2013).
Other similar efforts focused on defining entirely new principles or extending
the CIA triad, such as \autocite{NISTSP800-160}. 
%What is of interest for our
%argument is that, to the best of our knowledge, all of the approaches that aim
%at improving the CIA triad are besed on motivations related to empirical evidences. On the contrary,
%We now define (in Section~\ref{sec:properties}) the CIA triad for an agent
%defined in the $\abftheory$-theory and we test if (i) other properties are
%allowed in the $\abftheory$-theory, and (ii) if and how the CIA triad can be
%detailed in the $\abftheory$-theory.
In \autocite{Anderson1972report,Samonas2014cia}, CIA are defined as follows.
\begin{itemize}
	\item \emph{Unauthorized information release}: an unauthorized person is able
		to read and take  advantage  of  information  stored  in  the
		computer.  This  category of concern  sometimes  extends  to
		``traffic  analysis,''  in  which  the intruder  only observes
		the  patterns  of  information  use.  From  those patterns,
		the  intruder can   infer   some   information   content.
		This category   also   includes   the unauthorized use of a
		proprietary program.  (Confidentiality or Secrecy) 
	\item \emph{Unauthorized  information  modification}:  an  unauthorized person
		is  able  to make changes in stored information -- a form  of
		sabotage.  It should be noted that in the case of this kind of
		violation, the intruder does not necessarily see the
		information he has changed.  (Integrity)
	\item \emph{Unauthorized  denial  of  use}:  an  intruder  can  prevent  an
		authorized  user  from referring to, or from modifying
		information, even though the intruder may not be able to refer
		to, neither modify the information themselves. (Availability)
\end{itemize}

We now want to generalize the CIA triad to agents and systems in the
$\abftheory$-theory (and not just Information). Given that we are currently
dealing with the step that moves from specification to design, we consider
architectural properties. For the sake of simplicity, we revert the order and
start from availability.

\Paragraph{Availability and Integrity (Architecture Security)}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{client-server.pdf}
	\caption{Client-Server paradigm in $\abftheory$-theory}
	\label{fig:client-server}
\end{figure}
Availability, again, is the denial of use of a resource. In the $\abftheory$-theory, 
in order to prevent a resource to be available, there
exists only (i.e. inclusively) the following cases
that we illustrate using a client-server paradigm (depicted in Figure~\ref{fig:client-server}).
\begin{enumerate}
	\item\label{case:srv1} The resource on the server cannot be found, so that it is
		possible for the client to contact the server and for the server
		to send a response back, but the output-port does not receive the
		necessary information. This may be due to a software error such
		that the functional architecture doesn't output a response, or
		a problem in the flow of information (i.e. the functional
		architecture doesn't receive the necessary information from
		other resources), or an hardware failure \&c. This can be formalized
		as an issue to be found in the relation between the beliefs produced by the functional
		architecture and the ones received by the output port, i.e.
		$\rcc(\behaviorRegion_s,\{\text{res}_0\})$ or 
		$\rcc(\beliefRegion_s,\{\text{res}_0\})$ 
	\item\label{case:srv2} The server hosting the resource is down, and then the server
		cannot output responses (i.e. insecure output port due to drop-related issue) or receive
		requests (insecure input port due to drop-related issue) or both.
	\item\label{case:srv3} The client cannot properly compute request (symmetric to Case~\ref{case:srv1})
	\item The client is down, symmetric to Case~\ref{case:srv2}
	\item The channel is down due to a drop related issue in one of the two channels 
\end{enumerate}
%All the cases but Case~\ref{case:srv1} and Case~\ref{case:srv3}, tell us how to map the
%property of availability over the weaknesses of ports and communications.  The
%Cases~\ref{case:srv1} and~\ref{case:srv3}, are exceptions because the formulas $res$ and $req$ 
%detail the specification with a singleton instead of a region of formulas (or, better, $|res|$ is equal to the one of the
%base).
%In other words, a channel, a port, an entity, or a functional block are
%Fact (stated in a factorial way) and not Beliefs; what they produce or 
%their non-specified internals are Beliefs.  In fact, we never assume an
%entity not to be in the design implementing the specification.  Similarly, when a
%functional block produces some information it produces a Belief, unless this Belief if detailed in the specification.
%For example, the server produces the Belief $res$ but the Belief given that can only be in $EQ$
%relation with the Fact $res$ (in contrast other Belief may not); therefore, $res$ is not really a belief but a Fact. 
%$res$ as a Fact is something that
%exists in the specification, while the Belief of $res$ in one of the possible
%designs may not exist. 
We shall, then, distinguish between two cases, as we mentioned beforehand:
agent (or system) and Information (which we call Infosec) availability. 
\begin{definition}{\bf Agent-Availability --}\label{def:agent-a}
when the property of availability is expressed over an agent or a system, the
	list of possible designs do not include those in which there exist:
	drop ports, or drop channels/functional-blocks.
\end{definition}
\begin{definition}{\bf Infosec-Availability --}\label{def:infosec-c}
when the property of availability is expressed
	over a formula, the list of possible designs that violates the
	availability property is reduced to the part of the system that
	does not influence that specific formula.
\end{definition}

\begin{definition}{\bf Agent-Integrity --}\label{def:agent-a}
when the property of integrity is expressed over
	an agent or a system, the list of possible designs 
	do not include those in which there exist: insert or inject ports, 
	or inert or inject channels/functional-blocks. 
\end{definition}
\begin{definition}{\bf Infosec-Integrity --}\label{def:infosec-c}
when the property of integrity is expressed
	over a formula, the list of possible designs that violates the
	integrity property is reduced to the part of the system that
	influences that specific variable.
\end{definition}

While availability and integrity are architectural property, meaning that they
can be expressed over the behavior of a port or a channel (as constituent of
the physical or functional architecture), confidentiality is not.
Confidentiality states that an information shall not be understood and not that
the information shall not be retrieved. So, if a port leaks an entire message,
there is no confidentiality issue in general, unless that message was not
encrypted at all, in which case the confidentiality leakage is straightforward. 
On the other hand, if the
information is not provided or altered there is an availability or integrity
issue. A similar argument can be proposed for integrity sub-properties such as
authenticity or non-repudiation. No wonder why it is often stated that
availability and integrity are the first properties to be considered in CPS
while confidentiality takes the first place when dealing with security
protocols. In fact, integrity is often assumed by pattern-matching (e.g. in
AVANTSSAR \autocite{avantssar}) and availability is hardly ever considered in
protocol verification. The question is, can we express properties such as
confidentiality, authentication, or non-repudiation as architectural properties
in $\abftheory$-theory? Confidentiality is based on the concept 
of secrecy so we shall first start from describing what secrecy is and how it
can be used to guarantee confidentiality in a system.

\Paragraph{Secrecy, Authenticity, and Key Agreement (Cryptographic Security)}\label{sec:encryption}
As Maurer puts it (\autocite{Maurer1999information}), there exist two types of
cryptographic security (i.e. scientific theories aiming at guaranteeing
security through the use of cryptographic functions): ``The security  of a
cryptographic system can rely either on the computational infeasibility of
breaking it (computational security), or on the theoretical impossibility of
breaking it, even using in infinite computing power (information-theoretic or
unconditional security)''. We are not currently interested in detailing the
difference between the two and we simplify it as follows. A
computationally-secure cryptographic function (usually called encryption
function) $E(\varphi)=e$ (where $\varphi$ is a plain-text and $e$ a
cipher-text) can be considered perfectly secure if a malicious agent that
obtains the result of the cryptographic function ($e$) has bounded
computational power, while unconditional secure cryptographic functions are
considered perfectly secure. In this context, security means that is is
impossible to calculate $\varphi$ from $e$, therefore impossible to compute
$D(e)=\varphi$.  As one can evince from \autocite{Shannon1948information}, the
commonality between the two types of cryptographic functions is that they both
rely on the assumption about the probabilistic behavior of the universe. They
do so, for the random (i.e. with high entropy
\autocite{Shannon1948information}) generation of the so called \emph{key}, a
piece of information, parametric to the cryptographic function, used to
guarantee the security. Therefore, we can assume that it is feasible for an
agent that knows $k$ to decrypt the cipher-text obtaining the clear-text (i.e. $D(k, E(k,\varphi))=\varphi$)
while it is impossible for any agent that has not the proper key. In this
case, the information is considered to be \emph{secret or confidential}.

\begin{definition}{\bf Infosec-Secrecy or Confidentiality --}\label{def:confidentiality}
	When an Assertion has been generated as an output by an
	agent, port, or functional block such that it is said (in a
	factorial way) to encrypt the input, that Assertion is considered
	confidential.
\end{definition}
The quality of the confidentiality of information (Assertions or Beliefs depending on 
the subsystem considered) is inversely proportional to the number of 
integrity issues of the subsystem.
We now discuss more in details what secrecy of Information is when 
dealing with functional blocks (Behavior) and Beliefs but a similar treatment can be done 
in the case of Channels and Assertions.

@@

\begin{definition}{\bf Secrecy of Functional Block and Architecture --}\label{def:secfun}
	Secrecy is preserved in a functional block if the input beliefs and output beliefs
	are in $EQ$ relation with the corresponding Facts mandated by the confidentiality/secrecy requirements.
	A functional architecture composed exclusively by confidential/secrecy-preserving functional blocks
	is considered confidential/secrecy-preserving.
\end{definition}

\Paragraph{Confidentiality Weaknesses}
In a functional block, there exists the following weaknesses in the functional
architecture, where $\beliefRegion_I$ and $\beliefRegion_O$ are input and
output Beliefs respectively, and $\factRegion_I$ and $\factRegion_O$ are
the corresponding Facts. 
\begin{itemize}
	\item $\eq{\beliefRegion_I}{\factRegion_I}$ and then only specified
		inputs can be fed to the functional block but:
	\begin{enumerate}[start=49, label={W\arabic*)}]
		\item\label{w:fb_eqdr} $\dr{\beliefRegion_O}{\factRegion_O}$, not all the specified
			outputs are produced. This may produce a secrecy issue if, for example,
			the functional block is responsible for generating an encryption key since
			if it is not produced the encryption of the Information may not be performed
		\item\label{w:fb_eqpo} $\po{\beliefRegion_O}{\factRegion_O}$, only some but not all of the specified
			outputs are produced along with some non-specified output are produced. This
			strightforwardly generates a secrecy when the functionality is 
			related to secrecy functional blocks since some outputs doesn't follow
			the requirements.
		\item $\pp{\beliefRegion_O}{\factRegion_O}$, not all the specified outputs are produced.
			This may pose a secrecy issue as in \ref{w:fb_eqdr}
		\item $\ppi{\beliefRegion_O}{\factRegion_O}$, not all the output have been specified.
			This may pose a secrecy issue as in \ref{w:fb_eqpo}
	\end{enumerate}
	\item $\po{\beliefRegion_I}{\factRegion_I}$, not all the specified inputs can be fed into the functional block
	\begin{enumerate}[start=53, label={W\arabic*)}]
		\item $\dr{\beliefRegion_O}{\factRegion_O}$
		\item $\po{\beliefRegion_O}{\factRegion_O}$
		\item $\pp{\beliefRegion_O}{\factRegion_O}$
		\item $\ppi{\beliefRegion_O}{\factRegion_O}$
		\item $\eq{\beliefRegion_O}{\factRegion_O}$ this case implies
			that somehow there is no input that generates an
			non-specified output but this is not because the inputs
			are secure 
	\end{enumerate}
	\item $\pp{\beliefRegion_I}{\factRegion_I}$, not all the specified
		inputs can be fed into the block
	\begin{enumerate}[start=58, label={W\arabic*)}]
		\item $\dr{\beliefRegion_O}{\factRegion_O}$
		\item $\po{\beliefRegion_O}{\factRegion_O}$
		\item $\pp{\beliefRegion_O}{\factRegion_O}$
		\item $\ppi{\beliefRegion_O}{\factRegion_O}$
		\item $\eq{\beliefRegion_O}{\factRegion_O}$
	\end{enumerate}
	\item $\ppi{\beliefRegion_I}{\factRegion_I}$, not all the inputs that
		can be fed into the functional block follows the specification
	\begin{enumerate}[start=63, label={W\arabic*)}]
		\item $\dr{\beliefRegion_O}{\factRegion_O}$
		\item $\po{\beliefRegion_O}{\factRegion_O}$
		\item $\pp{\beliefRegion_O}{\factRegion_O}$
		\item $\ppi{\beliefRegion_O}{\factRegion_O}$
		\item $\eq{\beliefRegion_O}{\factRegion_O}$
	\end{enumerate}
	\item $\dr{\beliefRegion_I}{\factRegion_I}$, no specified inputs can be
		fed into the functional block
	\begin{enumerate}[start=68, label={W\arabic*)}]
		\item $\dr{\beliefRegion_O}{\factRegion_O}$
		\item $\po{\beliefRegion_O}{\factRegion_O}$
		\item $\pp{\beliefRegion_O}{\factRegion_O}$
		\item $\ppi{\beliefRegion_O}{\factRegion_O}$
		\item $\eq{\beliefRegion_O}{\factRegion_O}$
	\end{enumerate}
\end{itemize}

\begin{hypothesis}{\bf System Security Design --}\label{hyp:security}
	A system security design is given by a precise system security
	specification over the physical and functional architectures, that
	uniquely, i.e.  tested against the range of design possible in the
	$\abftheory$-theory, defines the designs built on top of those
	requirements.
\end{hypothesis}

\begin{hypothesis}{\bf System Insecurity Design --}\label{hyp:insecurity}
	If, given a system security specification as a collection of
	requirements on the system, there exist
	a non-unique design that respect those requirements, the number of
	equivalent designs that fullfills the requirements quantitatively
	defines the magnitute of insecurity of a system design.
\end{hypothesis}

\subsection{Abstraction Level of a Specification in $\abftheory$-theory}
The level of abstraction is always a concern when it comes to the definition of
a system model.  In this paper, we justified our assumptions on the atomicity
of ports, channels, and functional blocks but nothing prevents a modeler to
consider other atomic element of the system specification and design.  Those
additional elements may detail the system and may change the syntactic sugar we
defined; however, it won't change the underlying (semantic) reasoning unless
another calculus is used (instead of RCC).  Furthermore, other Infosec
properties may be considered, such as authenticity or non-repudiation. We,
however, leave them as future development.
